Hunting experience shapes individual foraging specialization and predator-prey interactions in an online videogame

### 2023-05-31 manuscript/Chapter2-manuscript.Rmd
updated the methods. might need to revisit

In this study, we evaluated how hunting experience shapes predator foraging specialization and success using data from players in the online videogame *Dead by Daylight*. First, we investigate how predators develop their individual hunting expertise. We hypothesize that predators should differ in the development of their expertise if they encountered varying levels of difficulty with the prey that they pursued. For example, a predator may face greater difficulty than other individuals if it encountered elusive groups of prey more often. Second, we test the hypothesis that experience will shape individual foraging specialization. We define foraging tactics as the mean movement speed of the predator along a slow-fast continuum, and the level of individual foraging specialization as the intra-individual variance (i.e. IIV) in movement speed from one match to the next where low IIV translates to individual specialization. If experience reduces the costs of switching between low and high speeds, we predict that individuals (and thus the population) should all converge towards flexible speeds. If experience enables the refinement of the tactics to hunt specific types of prey, then all individuals may instead specialize in their speed. In both scenarios, among individual variation in IIV (i.e. individual specialization) should be low because everyone is either a specialist or a generalist, but the population variance should either increase (flexibility) or decrease (specialization). Alternatively, both processes may operate at the same time if behavioural interactions with the prey vary among predators, such that among individual variation in IIV should increase. In this case, we expect predators that experienced more predictable encounters with their prey (i.e. homogeneous groups across matches) to specialize in their speed, while predators that experienced unpredictable encounters with their prey (i.e. heterogeneous groups across matches) should adopt flexible movement speeds. If we detect such prey-dependent fine-tuning, then specialist and flexible hunters should attain equal success because both should have learned to optimize their hunting style to their prey.

@@

Our population consists of `r toString(format(length(unique(dat$predator_id))))` predator players with a total record of `r toString(formatC(length(unique(dat$match_id)), big.mark = " "))` matches. The predator-players' experience varied between `r toString(format(min(dat$total_xp_pred)))` and `r toString(format(max(dat$total_xp_pred)))` matches played. These matches lasted between `r toString(format(round(min(dat$game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$game_duration / 60))), digits = 2)`-min (mean = `r toString(format(round(mean(dat$game_duration / 60))), digits = 2)`-min). The following information is collected and reported for every match : the player's anonymous ID, its avatar (i.e. the predator character chosen with its specific skill-gameplay mechanics), the game environment, the predator-player's experience along with its speed, and the average speed of the group of prey it encountered.

We analyzed the predator's average speed and the average speed of the prey group encountered by the predator. The predator's average speed is measured as the average distance traveled per second during a match ($\overline{speed}$ = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))` m/s). We measured the preys' average speed as the average travel speed of the four individual prey within a match ($\overline{prey speed}$ = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` m/s). We defined hunting success as the number of prey captured during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`). Lastly, we defined the predator's cumulative experience as the number of matches played prior to the match being monitored. For example, the first match of a player would have a cumulative experience value of 0, while the tenth match would have a value of 9. We also categorized predators for each match by their experience based on the number of matches they played before. We labeled predators as novices for matches with less than 100 matches played, intermediate between 100 and 299 matches played, and advanced when cumulative experience was above 299 matches (max 499). Since we monitored all predator players throughout their experience, they appeared in all the three experience categories.

We recognize that we could have biased our analyses by retaining only individuals who played for at least 300 matches. For example, these individuals might be experienced videogame players and could thus already be playing optimally in their first matches in *DBD*. To verify that our sample was not biased, we compared a random sample of players that played either 20 to 50 matches, 51 to 100 matches, or 101 to 300 matches during the same timeframe as our sampled population. We then took the first 20 matches played by these players, including those from our sampled population, and compared their average speed using a Bayesian hierarchical linear model. We found that all four groups had similar average speeds (Appendix 2: Table S1-S2), which indicates an absence of bias due to data sampling.

@@

We tested whether predators varied in the development of their expertise by computing five Bayesian generalized additive mixed models (GAMM) with thin-plate regression splines, all of which estimated the relationship between hunting success (i.e. number of prey captured) and the predators' cumulative experience (i.e. number of matches played before the current match). We parameterized the models following the method of @Pedersen.etal2019. The first model was the simplest, with a common global smoothing function and random intercepts for the predator ID. In this model, we assume that predators have the same development of expertise, with the model estimating a trend for the average individual (i.e. global smoother). For the second model, we included varying group-level smoothers for the predator ID. Here, we assume that predators share a similar relationship between success and experience, but that this relationship can vary among individuals (e.g. predator 1 has a steeper curve than predator 2). This enabled us to test whether predators differed in the development of their expertise. In the third model, we kept the group-level smoothers for the predators, but removed the global smoother. This model assumes that predators do not share a common relationship between success and experience. The fourth and fifth models were a reproduction of the second and third models respectively, where we included the prey group's average speed to assess its effect on the relationship between success and experience. We included the standardized match duration and average prey rank (a proxy for prey skill) as covariates in all five models. The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank), and failing to account for it would prevent us from detecting a change in the predator's foraging success with experience.

We computed the five models using a modified version of the beta-binomial distribution implemented in "brms". Hunting success was estimated as the probability of capturing the four prey ($\mu_i$), drawn from a Beta distribution ($Beta(\mu_i, \phi)$) with mean ($\mu \in [0,1]$) and precision ($\phi > 0$) parameters. We used a logit link function to estimate $\mu_i$ where $\mu_i = \frac{exp(\eta_i)}{exp(\eta_i) + 1}$ and $\eta_i$ is the linear predictor, while the precision parameter ($\phi$) was estimated with an identity link. We used the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience. We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated standard deviation ($id \sim N(0,\ I\ \sigma_{id})$). We used weakly informative Gaussian priors for the intercept ($N(0,\ 0.5)$) and the global trend of cumulative experience ($N(0,\ 2)$). Based on previous results [@FraserFranco.etal2022], we defined a positive Gaussian prior on the precision parameter ($N(2,\ 0.5)$), a positive Gaussian prior ($N(1,\ 0.5)$) on the game duration because longer trials lead to greater success, and a negative Gaussian prior on prey speed ($N(-1,\ 0.5)$) because encountering faster prey is associated with lower success in this system. We employed weakly informative half-Gaussian priors on all the standard deviation parameters ($N(0, 0.5)$). We compared the models' predictive accuracies using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].

@@

We tested whether foraging behaviour changed with experience, and compared the success of generalists vs specialists, using a multivariate, double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@Mitchell.etal2016a]. For each level of experience (i.e. novice, intermediate, advanced), the model estimated the mean speed of every individual (which we call the mean part of the model), and the intra-individual standard deviation of speed of every individual (which we call the dispersion part of the model). From the mean part of the model, we could infer on among individual differences in foraging tactics (i.e. along the slow-fast continuum), while in the dispersion part of the model, we could infer on among individual differences in foraging specialization (i.e. intra-individual variability, IIV). We followed the same structure for the preys' speed. For the mean part, we tested whether individual predators differed in the average speed of the groups of prey encountered across the study. For the dispersion part, we tested whether individual predators differed in how (dis)similar were the groups of prey they encountered across the study (i.e. if resource heterogeneity was higher for some individuals compared to others). We controlled for the standardized average rank of the prey group for both the predator and the prey's speed (mean and dispersion). For hunting success, we quantified among individual differences in mean prey capture and controlled for the square-root of the game duration.

The model estimated the correlation between the individual identity random effect on the mean and on the dispersion within each trait (e.g. $cor(\sigma_{id_{m}\ pred}\ \sigma_{id_{d}\ pred})$) and among each trait (e.g. $cor(\sigma_{id_{m}\ pred}\ \sigma_{id_{d}\ prey})$) within a level of experience. In the first case, this allows us to assess, for example, whether predators that are on average slower/faster are more specialized or flexible. In the second case, it enables us to estimate, for example, whether predators that adopted a slower/faster (or more specialized/flexible) tactic encountered prey that were faster/slower, or if slower/faster predators had lower/greater hunting success.

The full model has the following form, with each equation repeated three times (i.e. one for each level of experience):

@@

# Prepare equations
eqs <- c(
  "speed_{pred} = X_{m}\\ b_{m} + M\\ env_{m} + N\\ av_{m} + Z\\ id_{m} + e",
  "log(\\sigma_{e,pred}) = X_{d}\\ b_{d} + Z\\ id_{d}",
  "speed_{prey} = X_{m}\\ b_{m} + M\\ env_{m} + N\\ av_{m} + Z\\ id_{m} + e",
  "log(\\sigma_{e,prey}) = X_{d}\\ b_{d} + Z\\ id_{d}",
  "success_{pred} = X_{m}\\ b_{m} + Z\\ id_{m} + e"
)
eqs_num <- c(
    "(eqn. 1.1)",
    "(eqn. 1.2)",
    "(eqn. 2.1)",
    "(eqn. 2.2)",
    "(eqn. 3)"
)

@@

# Customize table
my_theme <- function(x, ...) {
  x <- colformat_double(x, big.mark = " ",
                        decimal.mark = ".",
                        digits = 2)
  x <- border_remove(x)
  x <- delete_part(x, part = "header")
  x <- align(x, j = 1, align = "left", part = "body")
  x <- align(x, j = 2, align = "right", part = "body")
  x <- font(x, fontname = "Times New Roman", part = "body")
  x <- fontsize(x, size = 12, part = "body")
  x <- width(x, j = 1, width = 10, unit = "cm")
  x <- width(x, j = 2, width = 6.51, unit = "cm")
}

@@

where $env$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their incidence matrices $M$, $N$, and $Z$. $b$ is the vector of fixed effects with its incidence matrix $X$. The $m$ and $d$ subscripts indicate that an estimate is from the mean or dispersion part of the model, respectively. On the mean part, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($env \sim N(0,\ I\ \sigma_{env})$ and $av \sim N(0,\ I\ \sigma_{av})$). $I$ is the identity matrix, with $I\sigma$ indicating that the random effects are independently and identically distributed. The residuals are assumed to follow a Gaussian distribution ($e \sim N(0,\ \sigma_{e})$). On the dispersion part, the residuals vary among individuals, allowing us to estimate among individual differences in specialization. The individual identity random effects on both the mean and dispersion parts follow a multivariate Gaussian distribution $[\begin{array}{cc} id_m \\ id_d \end{array}] \sim MVN(0,\ \Sigma_{id})$ where $\Sigma_{id}$ is a 15x15 variance-covariance matrix. The parameters $\sigma_{env}$, $\sigma_{av}$, and $\sigma_{id}$, correspond to the among environment, among avatar, and among individual standard deviations, respectively.

We parameterized equations 1.1 to 2.2 with a Gaussian distribution family (predator and prey speed) and used a beta-binomial distribution family for equation 3 (predator hunting success). We used weakly informative Gaussian priors for the prey rank ($N(0,\ 1)$: eqn. 1.1 to 2.2) and game duration ($N(0.5,\ 0.5)$: eqn. 3). Based on previous results showing that the mean predator speed revolves around 3 m/s [@FraserFranco.etal2022], we applied a weakly informative Gaussian prior on the intercept for predator and prey speed ($N(3, 0.5)$: eqn. 1.1 and 2.1). Similarly, we used a weakly informative Gaussian prior on the intercept for the dispersion part ($N(0,1)$: eqn 1.2 and 2.2). For hunting success, we applied a positive Gaussian prior on the precision parameter ($N(2,\ 1)$: eqn. 3) and a negative Gaussian prior ($N(-4, 1)$: eqn 3) on the intercept because hunting success should be close to 0 at the lowest game duration. For every predicted variable, we applied a weakly informative half-Gaussian prior ($N(0,\ 1)$) on the random effects for the mean part and the dispersion part of the model. We used a regularizing $LKJ(2)$ prior on the correlation matrix.

@@

Out of all five models, the two that best predicted the data, with very similar expected log pointwise densities (elpd), were the models accounting for the prey group's speed (Table 1). Predators differed substantially in the relationship between hunting success and cumulative experience (i.e. expertise: Figure 1A-B). We found evidence that these differences were in part mediated by prey speed because individuals had distinct patterns after we controlled for the mean speed of the prey groups compared to when we did not (Figure 1A-B). For instance, many individual curves shifted upwards. Precisely, the percentage of individuals that displayed a >0.5 increase in success changed from `r toString(scales::percent(percent_tab1[2,]$percentage, accuracy = 0.1))` to `r toString(scales::percent(percent_tab1[5,]$percentage, accuracy = 0.1))` after we accounted for prey speed (Appendix S1: Figure S1A). In this model (i.e. Figure 1B-C), `r toString(scales::percent(percent_tab1[4,]$percentage, accuracy = 0.1))` of the population showed a >0.5 decrease in success (Appendix S1: Figure S1B), and the remaining `r toString(scales::percent(percent_tab1[6,]$percentage, accuracy = 0.1))` displayed little to no change (between -0.5 and 0.5) in success across experience (Appendix S1: Figure S1C).

Moreover, all models where we did not account for prey speed had a global trend of predator experience that was nearly flat (results not shown). Yet, we see that there is an increase up to 13% in the probability of capturing all prey with experience in the population when we account for prey speed (Figure 1C).

@@

It is likely that predators were also driving changes in prey behaviour because most predator-prey behavioural relationships remained stable even though half of the population switched from a specialist to a flexible strategy and vice-versa across experience. This implies that the prey were probably also learning how to avoid predation through repeated interactions. Our results concord with what @Mougi.etal2011 define as a matching response relationship, because faster-specialist and slower-flexible hunters preyed upon different prey, but they both achieved equal success. These types of reciprocal responses to interactions have been observed in other predator-prey systems [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013], but their broader consequences remain unclear. Assuming that prey also learned during the interaction, which has been shown across many taxa [refs], we can deduce that learning from reciprocal interactions may contribute in stabilizing predator-prey systems, similar to Red Queen dynamics [@brockhurst2014].

@@

**Figure 1.** Among individual differences in the development of hunting expertise. The predators' hunting success (i.e. the probability of capturing the four prey) is on the y axis, and the predators' cumulative experience (i.e. the number of matches played prior to each observation) is on the x axis. Each fitted curve represents an individual predator. (A) A generalized additive mixed model where we do not control for prey speed (B) A generalized additive mixed model where we control for prey speed.

>>>>

In this study, we evaluated how hunting experience shapes predator foraging specialization and success using data from players in the online videogame *Dead by Daylight*. First, we investigate how predators develop their individual hunting expertise. We hypothesize that predators should differ in the development of their expertise if they encountered varying levels of difficulty with the prey that they pursued. For example, a predator may face greater difficulty than other individuals if it encountered elusive groups of prey more often. Second, we test the hypothesis that experience will shape individual foraging specialization. We define foraging tactics as the mean movement speed of the predator along a slow-fast continuum, and the level of individual foraging specialization as the intra-individual variance (i.e. IIV) in movement speed from one match to the next, where low IIV translates to individual specialization. If experience reduces the costs of switching between low and high speeds, we predict that individuals (and thus the population) should all converge towards flexible speeds. If experience enables the refinement of the tactics to hunt specific types of prey, then all individuals may instead specialize in their speed. In both scenarios, among individual variation in IIV (i.e. individual specialization) should be low because everyone is either a specialist or a generalist, but the population variance should either increase (flexibility) or decrease (specialization). Alternatively, both processes may operate at the same time if behavioural interactions with the prey vary among predators, such that among individual variation in IIV should increase. In this case, we expect predators that experienced more predictable encounters with their prey (i.e. similar groups across matches) to specialize in their speed, while predators that experienced unpredictable encounters with their prey (i.e. heterogeneous groups across matches) should adopt flexible movement speeds. If we detect such prey-dependent fine-tuning, then all hunters along the flexible-specialist continuum should attain equal success probably because they learned from experience how to adjust their hunting style to their prey.

@@

Our population consists of `r toString(format(length(unique(dat$predator_id))))` predator players with a total record of `r toString(formatC(length(unique(dat$match_id)), big.mark = " "))` matches. The predator-players' experience varied between `r toString(format(min(dat$total_xp_pred)))` and `r toString(format(max(dat$total_xp_pred)))` matches played. These matches lasted between `r toString(format(round(min(dat$game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$game_duration / 60))), digits = 2)` min (mean = `r toString(format(round(mean(dat$game_duration / 60))), digits = 2)` min). The following information is collected and reported for every match : the player's anonymous ID, its avatar (i.e. the predator character chosen with its specific skill-gameplay mechanics), the game environment, the predator-player's experience along with its speed, and the average speed of the group of prey it encountered.

We analyzed the predator's average speed and the average speed of the prey group encountered by the predator. The predator's average speed is measured as the average distance traveled per second during a match (mean= `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))` m/s). We measured the preys' average speed as the average travel speed of the four individual prey within a match (mean = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` m/s). We defined hunting success as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`). Lastly, we defined the predator's cumulative experience as the number of matches played prior to the match being monitored. For example, the first match of a player would have a cumulative experience value of 0, while the tenth match would have a value of 9. We also categorized predators for each match based on their cumulated experience. We labeled predators as novices for matches where they had cumulated less than 100 matches, intermediate for matches where they had cumulated between 100 and 299 matches, and advanced for matches where they had cumulated more than 299 matches (max 499). Since our goal was to monitor predator players throughout their experience and that they all played at least 300 matches, they appeared in all the three experience categories.

We recognize that we could have biased our analyses by retaining only individuals who played for at least 300 matches. For example, these individuals might be experienced videogame players and could thus already be playing like experts in their first matches in *DBD*. To verify that our sample was not biased, we compared a random sample of players that played either 20 to 50 matches, 51 to 100 matches, or 101 to 300 matches during the same timeframe as our sampled population. We then took the first 20 matches played by these players, including those from our sampled population, and compared their average speed using a Bayesian hierarchical linear model. We found that all four groups had similar average speeds as predators (Appendix 2: Table S1-S2), which indicates an absence of bias due to data sampling.

@@

We tested how prey influence the development of predator expertise by computing five Bayesian generalized additive mixed models (GAMM) with thin-plate regression splines, all of which estimated the relationship between hunting success (i.e. number of prey consumed) and the predators' cumulative experience (i.e. number of matches played before the current match). We parameterized the models following the method of @Pedersen.etal2019. The first model was the simplest, with a common global smoothing function and random intercepts for the predator ID. In this model, we assume that predators have the same development of expertise, with the model estimating a trend for the average individual (i.e. global smoother). For the second model, we included varying group-level smoothers for the predator ID. Here, we assume that individual predators share a similar relationship between success and experience, but that this relationship can vary among them (e.g. predator 1 has a steeper curve than predator 2). This enabled us to test whether predators differed in the development of their expertise. In the third model, we kept the group-level smoothers for the individual predators, but removed the global smoother. This model assumes that predators do not share a common relationship between success and experience. The fourth and fifth models were a reproduction of the second and third models respectively, where we included the prey group's average speed to assess its effect on the relationship between success and experience. We included the standardized match duration and average prey rank (a proxy for prey skill) as covariates in all five models. The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank), and failing to account for it would prevent us from detecting a change in the predator's foraging success with experience.

We computed the five models using a modified version of the beta-binomial distribution implemented in "brms". Hunting success was estimated as the probability of consuming the four prey ($\mu_i$), drawn from a Beta distribution ($Beta(\mu_i, \phi)$) with mean ($\mu \in [0,1]$) and precision ($\phi > 0$) parameters. We used a logit link function to estimate $\mu_i$ where $\mu_i = \frac{exp(\eta_i)}{exp(\eta_i) + 1}$ and $\eta_i$ is the linear predictor, while the precision parameter ($\phi$) was estimated with an identity link. We used the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience. We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated standard deviation ($id \sim N(0,\ I\ \sigma_{id})$). We used weakly informative Gaussian priors for the intercept ($N(0,\ 0.5)$) and the global trend of cumulative experience ($N(0,\ 2)$). Following @FraserFranco.etal2022, we defined a positive Gaussian prior on the precision parameter ($N(2,\ 0.5)$), a positive Gaussian prior ($N(1,\ 0.5)$) on the game duration because longer trials lead to greater success, and a negative Gaussian prior on prey speed ($N(-1,\ 0.5)$) because encountering faster prey is associated with lower success in this system. We employed weakly informative half-Gaussian priors on all the standard deviation parameters ($N(0, 0.5)$). We compared the models' predictive accuracies using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].

@@

We tested whether foraging behaviour changed with experience, and compared the success of flexible vs specialist hunters, using a multivariate double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@Mitchell.etal2016a]. We fitted the model on the predator's speed ($Y_{1}$), the prey's speed ($Y_{2}$), and the predator's hunting success ($Y_{3}$), which allowed us to simultaneously estimate three distinct components for each experience level. The first component is among individual variation in mean speed and success (the mean part of the model), allowing to test for individual differences in tactic use (i.e. along the slow-fast continuum), in the mean speed of the prey encountered, and in prey consumption. The second component is among individual variation in intra-individual behavioural variation (IIV) (the dispersion part of the model), allowing us to test for individual differences in foraging specialization and in how (dis)similar was the speed of the groups of prey encountered (i.e. if resource heterogeneity was higher for some individuals compared to others). The third component consists of pairwise comparisons between the individual identity random effect variances on the mean and dispersion part of the model across traits and experience levels, computed as a 15x15 (co)variance matrix. This allows us to assess whether predators that are on average slower/faster are more specialized or flexible, whether predators that adopted a slower/faster (or more specialized/flexible) tactic encountered prey that were faster/slower, and whether slower/faster predators had lower/greater hunting success.

We controlled for the standardized average rank of the prey group for both the predator and the prey's speed on both the mean and the dispersion parts of the model. We included random effects for the game environment, the predator avatar, and the individual predator identity on the mean part of the model, and an individual identity random effect exclusively on the dispersion part. For hunting success, we modeled the mean part only and controlled for the standardized mean prey rank and game duration, and included an individual identity random effect.

The model can be written as:

@@

# Prepare equations
eqs <- c(
  "Y_{1}(T_{j}) = X_{1}(T_{j})\\ b_{1}(T_{j}) + M_{1}(T_{j})\\ en_{1}(T_{j}) + N_{1}(T_{j})\\ av_{1}(T_{j}) + Z_{1}(T_{j})\\ id_{1}(T_{j}) + e_{1}(T_{j})",
  "log(\\sigma_{e_{Y_{1}(T_{j})}}) = X_{d1}(T_{j})\\ b_{d1}(T_{j}) + Z_{d1}(T_{j})\\ id_{d1}(T_{j})",
  "Y_{2}(T_{j}) = X_{2}(T_{j})\\ b_{2}(T_{j}) + M_{2}(T_{j})\\ en_{2}(T_{j}) + N_{2}(T_{j})\\ av_{2}(T_{j}) + Z_{2}(T_{j})\\ id_{2}(T_{j}) + e_{2}(T_{j})",
  "log(\\sigma_{e_{Y_{2}(T_{j})}}) = X_{d2}(T_{j})\\ b_{d2}(T_{j}) + Z_{d2}(T_{j})\\ id_{d2}(T_{j})",
  "Y_{3}(T_{j}) = X_{3}(T_{j})\\ b_{3}(T_{j}) + Z_{3}(T_{j})\\ id_{3}(T_{j}) + e_{3}(T_{j})"
)
eqs_num <- c(
    "(1.1)",
    "(1.2)",
    "(2.1)",
    "(2.2)",
    "(3)"
)

@@

# Customize table
my_theme <- function(x, ...) {
  x <- colformat_double(x, big.mark = " ",
                        decimal.mark = ".",
                        digits = 2)
  x <- border_remove(x)
  x <- delete_part(x, part = "header")
  x <- align(x, j = 1, align = "left", part = "body")
  x <- align(x, j = 2, align = "right", part = "body")
  x <- font(x, fontname = "Times New Roman", part = "body")
  x <- fontsize(x, size = 12, part = "body")
  x <- width(x, j = 1, width = 15.25, unit = "cm")
  x <- width(x, j = 2, width = 1.26, unit = "cm")
}

@@

where $j$ is the index of the experience levels. The model is fitted on $n$ experience levels ($n = 3$) denoted by $T_{j}$, where $j$ ranges from 1 to $n$, being the novice, intermediate, and advanced levels. The $b$ terms are vectors of fixed effects with their incidence matrices $X$. The terms $en$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their incidence matrices $M$, $N$, and $Z$. The $d$ subscript indicates that a term is from the dispersion part of the model. On the mean part for all traits and experience levels, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($env \sim N(0,\ I\ \sigma_{env})$ and $av \sim N(0,\ I\ \sigma_{av})$). $I$ is the identity matrix, with $I\sigma$ indicating that the random effects are independently and identically distributed. The residuals are assumed to follow a Gaussian distribution ($e \sim N(0,\ \sigma_{e})$). The individual identity random effects on both the mean and dispersion parts across all response variables and experience levels are indexed in vector $u$. The vector $u$ of individual identity random effects follows a multivariate Gaussian distribution $u \sim MVN(0,\ \Sigma)$ where $\Sigma$ is a 15x15 (co)variance matrix. We parametrized equations 1.1 to 2.2 with a Gaussian distribution family and used a beta-binomial distribution family for equation 3.

We used weakly informative Gaussian priors for the prey rank ($N(0,\ 1)$: eqn. 1.1 to 2.2) and game duration ($N(0.5,\ 0.5)$: eqn. 3). Based on previous results showing that the mean predator speed revolves around 3 m/s [@FraserFranco.etal2022], we applied a weakly informative Gaussian prior on the intercept for predator and prey speed ($N(3, 0.5)$: eqn. 1.1 and 2.1). Similarly, we used a weakly informative Gaussian prior on the intercept for the dispersion part ($N(0,1)$: eqn 1.2 and 2.2). For hunting success, we applied a positive Gaussian prior on the precision parameter ($N(2,\ 1)$: eqn. 3) and a negative Gaussian prior ($N(-4, 1)$: eqn 3) on the intercept because hunting success should be close to 0 at the lowest game duration. For every predicted variable, we applied a weakly informative half-Gaussian prior ($N(0,\ 1)$) on the random effects for the mean part and the dispersion part of the model. We used a regularizing $LKJ(2)$ prior on the correlation matrix.

@@

Out of all five GAMM models, the two that best predicted the data, with very similar expected log pointwise densities (elpd), were the models accounting for the prey group's speed (Table 1). Predators differed substantially in the relationship between hunting success and cumulative experience (i.e. expertise: Figure 1A-B). We found evidence that these differences were in part mediated by prey speed because individuals had distinct patterns after we controlled for the mean speed of the prey groups compared to when we did not (Figure 1A-B). For instance, many individual curves shifted upwards. Precisely, the percentage of individuals that displayed a >0.5 increase in success changed from `r toString(scales::percent(percent_tab1[2,]$percentage, accuracy = 0.1))` to `r toString(scales::percent(percent_tab1[5,]$percentage, accuracy = 0.1))` after we accounted for prey speed (Appendix S1: Figure S1A). In this model (i.e. Figure 1B-C), `r toString(scales::percent(percent_tab1[4,]$percentage, accuracy = 0.1))` of the population showed a >0.5 decrease in success (Appendix S1: Figure S1B), and the remaining `r toString(scales::percent(percent_tab1[6,]$percentage, accuracy = 0.1))` displayed little to no change (between -0.5 and 0.5) in success across experience (Appendix S1: Figure S1C).

Moreover, all models where we did not account for prey speed had a global trend of predator experience that was nearly flat (results not shown). Yet, we see that there is an increase up to 13% in the probability of consuming all prey with experience in the population when we account for prey speed (Figure 1C).

@@

It is likely that predators were also driving changes in prey behaviour because most predator-prey behavioural relationships remained stable even though half of the population switched from a specialist to a flexible strategy and vice-versa across experience. This implies that the prey were probably also learning how to avoid predation through repeated interactions. Our results concord with what @Mougi.etal2011 define as a matching response relationship, because faster-specialist and slower-flexible hunters preyed upon different prey, but they both achieved equal success. These types of reciprocal responses to interactions have been observed in other predator-prey systems [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013a], but their broader consequences remain unclear. Assuming that prey also learned during the interaction, which has been shown across many taxa [refs], we can deduce that learning from reciprocal interactions may contribute in stabilizing predator-prey systems, similar to Red Queen dynamics [@brockhurst2014].

@@

**Figure 1.** Among individual differences in the development of hunting expertise. The predators' hunting success (i.e. the probability of consuming the four prey) is on the y axis, and the predators' cumulative experience (i.e. the number of matches played prior to each observation) is on the x axis. Each fitted curve represents an individual predator. (A) A generalized additive mixed model where we do not control for prey speed (B) A generalized additive mixed model where we control for prey speed.
